\bf Title here

### 2020-05-26 paper/paper.Rmd
reorder sections and plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(ferrn)
library(patchwork)
library(ggrepel)

load(here::here("data/temp.rda"))
load(here::here("data/data_mult.rda"))
load(here::here("data/holes_1d_geo.rda"))
load(here::here("data/holes_1d_geo_polish.rda"))
load(here::here("data/holes_2d_geo.rda"))
load(here::here("data/holes_2d_better.rda"))
load(here::here("data/holes_2d_better_max_tries.rda"))
load(here::here("data/holes_2d_better_random.rda"))
load(here::here("data/holes_2d_geo_polish.rda"))
load(here::here("data/holes_2d_better_polish.rda"))
load(here::here("data/holes_2d_better_max_tries_polish.rda"))
load(here::here("data/holes_2d_better_random_polish.rda"))
load(here::here("data/holes_2d_pos.rda"))
load(here::here("data/interrupt_yes.rda"))
load(here::here("data/interrupt_no.rda"))

@@

```{r}
knitr::include_graphics(path = here::here("figures/tour_path_new.png"))
```

@@

```{r eval = FALSE, echo = TRUE}
animation <- function(){

@@

```{r}
origin_dt_bi <- data_mult %>% 
  dplyr::select(-x3) %>% 
  gather(names, values) %>%
  mutate(names = as_factor(names))

@@

```{r eval = FALSE}
set.seed(123456)
holes_1d_geo <- animate_dist(data, tour_path = guided_tour(holes(), d = 1,
                                           search_f =  search_geodesic),
                  rescale = FALSE, verbose = TRUE)

@@

```{r echo = TRUE}
holes_1d_geo %>% head(5)
```

@@

```{r echo = TRUE}
holes_2d_better %>% head(5) 
```

# Visual methods

Given all the information of interest in a global object, the next thing is to design its visual representation that can diagnose our algorithm. In an iterative algorithm, one would be interested to know how one parameter changes as the algorithm iterates. The parameter could be could be the decision variable, the value of the optimisation function or other parameter that facilitate the algorithm. In projectio pursuit guided tour, apart from the decision variable projection basis, the value of index function (`index_val`), we are also interested to explore the effect the different searching methods, the neighbourhood parameter alpha, and the stage a particular observation is in (`info`). These are the variables that will be mapped into the diagnostic plot. The global object also has its time series nature since the observations are recorded as the algorithm progresses and thus can't be switch in rows. This time series structure is always hierachical and nested since each row can be labelled with the smallest unit `id` and up by the iterative structure of the algorithm. Take our example, in the global object, each row has an `id` label which is the smallest unit the observation is ordered. A larger ordering unit is `tries` since it is updated everytime a new target basis is found. A nested ordering unit is `loop`, which increases by one as searching method iterates and starts over at a new `tries`. These features explain the definition of the global object for projection pursuit guided tour in Figure \@ref(fig:glb-obj).

```{r glb-obj, out.width= "100%", out.height="20%", fig.cap="this is xxxx"}
knitr::include_graphics(path = here::here("figures/global_obj.png"))
```

*The examples and results below still need to be modified as the development / modification of both ferrn and tourr package*.

@@

A comparison of using scatter plot (all point geometry) and my new design is shown in Figure \@ref(fig:explore-all-search). As we can see the points for the first few tries on hte scatter plot are all squeezed in a tiny region, being nearly unseeable. While the plot on the right balances out the points in each `tries`. By linking the updating points for each `tries`, we observe that the largest improvement occurs in `tries = 5` where the number of searching points dramastically increased from 11 points in `tries = 4` to 86 points in `tries = 5`.

```{r explore-all-search, fig.cap="This is xxx"}
dt <- holes_2d_better_max_tries %>%
  filter(info != "interpolation") %>% 
  mutate(id = row_number())

@@

EXAMPLE: prevention on the decrese of interpolated value - interruption

EXAMPLE: comparison of interpolation in noisy index function

@@

```{r}
# points is always included in the newest version
p1 <- holes_2d_better %>% 
  filter(info == "interpolation") %>% 
  ggplot(aes(x = tries, y = index_val, col = as.factor(tries))) +
  geom_point() + 
  geom_line(aes(group = 1))

@@

EXAMPLE: polishing - add method : compare with max.tries and without for search_better.

EXAMPLE: add alpha: compare the cooling system of the neighbourhood parameter in serach_better & search_posse.

```{r echo = TRUE}
nrow(holes_2d_better_max_tries)
nrow(holes_2d_pos)
```

```{r}
dt <- holes_2d_better_max_tries %>%
  filter(info != "interpolation") %>% 
  mutate(id = row_number())

p1 <- dt %>%
  ggplot(aes(x = as.factor(tries), y = alpha, col = as.factor(alpha))) +
  geom_jitter() +
  geom_line(data = dt %>% group_by(tries) %>% filter(index_val == max(index_val)),
            aes(group = 1)) + 
  theme(legend.position = "none")

p2 <- dt %>%
  ggplot(aes(x = as.factor(tries), y = alpha, col = as.factor(alpha))) +
  geom_jitter() +
  geom_line(data = dt %>% group_by(tries) %>% filter(index_val == max(index_val)),
            aes(group = 1))  + 
  theme(legend.position = "none")

```{r echo = TRUE}
holes_1d_geo %>% explore_proj_pca() 
```

# Animating plots

```{r echo = TRUE, eval = FALSE}
holes_1d_geo %>% explore_proj_pca(animate = TRUE)
```

# Finding errors and developing improvements

The visualisation methods introduced above allow us to assess the performance of each optimisation routine and thus provide improvments.

## Interrupt

The left panel of Figure \@ref(fig:interruption) presents the trace plot of the interpolated basis using `search_better` to optimise the holes index (2D projection using the larger dataset). Tour interpolates from the current basis to the target basis, which has been found to have a higher index value by projection pursuit. The target basis will then be sent to the projection pursuit as the current basis to find the next target basis. We can observe from the plot that there are basis with even higher index value on the interpolation path. These bases could be used to search for new basis in the next round. Therefore, an interruption is constructed to only take interpolated basis up to the point where the index value stops increasing and the last basis is taken as the current basis for the next round of search. After implementing the interruption, the tracing plot with the same configuration is shown on the right panel. Rather than interpolate to the target basis, the interruption interrupt the process after id = 60 and proceeds the next round of search from the interpolated basis. Taking advantage of the interpolated basis results in a higher index value in the end with fewer steps.

```{r interruption, fig.cap = "\\label{interruption} Trace plots of the interpolated basis with and without the interruption. The interruption stops the interpolation when the index value starts to decrease, see the difference at id being around 60. The implementation of the interuption finds an ending basis with higher index value using fewer steps. "}
p1_anno <- interrupt_no %>% filter(info == "interpolation") %>% mutate(id = row_number()) %>% filter(id %in% c(44, 60, 62)) %>% 
  mutate(anno = c("current basis", "interpolated basis", "target basis"))

p1 <- interrupt_no %>% mutate(id = row_number() - 1) %>% explore_trace_interp() + ggtitle("without interruption") + 
  geom_point(data = p1_anno) + 
  geom_label_repel(data = p1_anno, aes(label = anno), box.padding = 0.5) + ylim(0.8, 0.9) + xlim(0, 80)

p2 <- interrupt_yes %>% explore_trace_interp() + ggtitle("with interruption") + ylim(0.8, 0.9) + xlim(0, 80)

Further the case when the index function is not smooth, the interpolation may not attain -> modification

## Polish

In principle, all the optimisation routines should present the same output on the same problem. In Figure \@ref(fig:trace-compare), red dots shows the trace of the interpolated basis using `search_geodesic` and `search_better` (with max.tries = 100), respectively, on the 2D projection problem. We can observe that they attain slightly different ending index value, which is not ideal. This motivates the creation of a polishing search that polishes the ending basis and achieves unity on different methods.

```{r}
p1 <- bind_rows(holes_2d_geo, holes_2d_geo_polish) %>% 
  explore_trace_interp(point = TRUE) + ggtitle("search_geodesic")

p2 <- bind_rows(holes_2d_better_max_tries, holes_2d_better_max_tries_polish) %>% 
  explore_trace_interp(point = TRUE) + ggtitle("search_better")

@@

```{r eval = FALSE, echo = TRUE}
set.seed(123456)
holes_2d_geo <- animate_xy(data_mult[,c(1,2, 7:10)],tour_path = 
                             guided_tour(holes(), d = 2, 
                                         search_f = tourr:::search_geodesic),
                           rescale = FALSE, verbose = TRUE)

@@

The following example conducted a 2D projection on the larger dataset using search better with different configurations. `max.tries` is a hyperparameter that controls the maximum number of try without improvement and its default value is 25. As shown in Figure \@ref(fig:trace-compare), after polishing, both trials attain the same index value. However, a small `max.tries` of 25 is not sufficient for the algorithm to find the true maximum. This is because 25 tries is not sufficient for the 2D searching space.

```{r trace-compare, fig.cap="Breakdown of index value when using different max.tries in search better in conjunction with search polish. Both attain the same final index value after the polishing while using a max.tries 25 is not sufficient to find the ture maximum."}

p1 <- bind_rows(holes_2d_better, holes_2d_better_polish) %>% 
  explore_trace_interp(point = TRUE) + ggtitle("max.tries = 25")

p2 <- bind_rows(holes_2d_better_max_tries, holes_2d_better_max_tries_polish) %>% 
  explore_trace_interp(point = TRUE) + ggtitle("max.tries = 500")

@@

## posse?

search_better annd search_geodesic methods are not doing good on 2d projection -> see the simple case above: abs best is 0.96 while they only get to 0.88-ish. Would be worse for higher dimension. thus search_posse. get 0.95 and then polish to 0.96 :)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(ferrn)
library(patchwork)
library(ggrepel)
```

```{r load-data}
files <- paste0("data/", list.files(here::here("data")))
purrr::walk(.x = files, ~load(here::here(.x), env = globalenv()))
```

@@

```{r tour-path}
knitr::include_graphics(path = here::here("figures/tour_path_new.png"))
```

@@

```{r algo,eval = FALSE, echo = TRUE}
animation <- function(){

@@

```{r origin-data}
origin_dt_bi <- data_mult %>% 
  dplyr::select(-x3) %>% 
  gather(names, values) %>%
  mutate(names = as_factor(names))

@@

```{r code, eval = FALSE}
set.seed(123456)
holes_1d_geo <- animate_dist(data, tour_path = guided_tour(holes(), d = 1,
                                           search_f =  search_geodesic),
                  rescale = FALSE, verbose = TRUE)

@@

```{r glb-obj-1, echo = TRUE}
holes_1d_geo %>% head(5)
```

@@

```{r glb-obj-2, echo = TRUE}
holes_2d_better %>% head(5) 
```

# Post-run static diagnostics plots

Given all the information of interest in a global object, the next thing is to design its visual representation that can diagnose our algorithm. In an iterative algorithm, one would be interested to know how one parameter changes as the algorithm iterates. The parameter could be could be the decision variable, the value of the optimisation function or other parameter that facilitate the algorithm. In projectio pursuit guided tour, apart from the decision variable projection basis, the value of index function (`index_val`), we are also interested to explore the effect the different searching methods, the neighbourhood parameter alpha, and the stage a particular observation is in (`info`). These are the variables that will be mapped into the diagnostic plot. The global object also has its time series nature since the observations are recorded as the algorithm progresses and thus can't be switch in rows. This time series structure is always hierachical and nested since each row can be labelled with the smallest unit `id` and up by the iterative structure of the algorithm. Take our example, in the global object, each row has an `id` label which is the smallest unit the observation is ordered. A larger ordering unit is `tries` since it is updated everytime a new target basis is found. A nested ordering unit is `loop`, which increases by one as searching method iterates and starts over at a new `tries`. These features explain the definition of the global object for projection pursuit guided tour in Figure \ref{fig:glb-obj}.

```{r glb-obj, out.width= "100%", out.height="20%", fig.cap="\\label{glb-obj}this is xxxx"}
knitr::include_graphics(path = here::here("figures/global_obj.png"))
```

@@

A comparison of using scatter plot (all point geometry) and my new design is shown in Figure \ref{fig:points}. As we can see the points for the first few tries on hte scatter plot are all squeezed in a tiny region, being nearly unseeable. While the plot on the right balances out the points in each `tries`. By linking the updating points for each `tries`, we observe that the largest improvement occurs in `tries = 5` where the number of searching points dramastically increased from 11 points in `tries = 4` to 86 points in `tries = 5`.

```{r points, fig.cap="\\label{points} This is xxx"}
dt <- holes_2d_better_max_tries %>%
  filter(info != "interpolation") %>% 
  mutate(id = row_number())

@@

*Example 1: Interruption* The left panel of Figure \ref{fig:interruption} presents the trace plot of the interpolated basis using `search_better` to optimise the holes index (2D projection using the larger dataset). Tour interpolates from the current basis to the target basis, which has been found to have a higher index value by projection pursuit. The target basis will then be sent to the projection pursuit as the current basis to find the next target basis. We can observe from the plot that there are basis with even higher index value on the interpolation path. These bases could be used to search for new basis in the next round. Therefore, an interruption is constructed to only take interpolated basis up to the point where the index value stops increasing and the last basis is taken as the current basis for the next round of search. After implementing the interruption, the tracing plot with the same configuration is shown on the right panel. Rather than interpolate to the target basis, the interruption interrupt the process after id = 60 and proceeds the next round of search from the interpolated basis. Taking advantage of the interpolated basis results in a higher index value in the end with fewer steps.

```{r interruption, fig.cap = "\\label{interruption}Trace plots of the interpolated basis with and without the interruption. The interruption stops the interpolation when the index value starts to decrease, see the difference at id being around 60. The implementation of the interuption finds an ending basis with higher index value using fewer steps. "}
p1_anno <- interrupt_no %>% filter(info == "interpolation") %>% mutate(id = row_number()) %>% filter(id %in% c(44, 60, 62)) %>% 
  mutate(anno = c("current basis", "interpolated basis", "target basis"))

p1 <- interrupt_no %>% mutate(id = row_number() - 1) %>% explore_trace_interp() + ggtitle("without interruption") + 
  geom_point(data = p1_anno) + 
  geom_label_repel(data = p1_anno, aes(label = anno), box.padding = 0.5) + ylim(0.8, 0.9) + xlim(0, 80) + 
  theme(legend.position = "none")

p2 <- interrupt_yes %>% explore_trace_interp() + ggtitle("with interruption") + ylim(0.8, 0.9) + xlim(0, 80) + 
  theme(legend.position = "none")

*Example 2: Noisy index function* Add an example on noisy function

@@

```{r interpolation}
# points is always included in the newest version
p1 <- holes_2d_better %>% 
  filter(info == "interpolation") %>% 
  ggplot(aes(x = tries, y = index_val, col = as.factor(tries))) +
  geom_point() + 
  geom_line(aes(group = 1))

@@

*Example 3: Polish* In principle, all the optimisation routines should present the same output on the same problem. In Figure \ref{fig:trace-compare}, red dots shows the trace of the interpolated basis using `search_geodesic` and `search_better` (with max.tries = 100), respectively, on the 2D projection problem. We can observe that they attain slightly different ending index value, which is not ideal. This motivates the creation of a polishing search that polishes the ending basis and achieves unity on different methods.

```{r polish}
p1 <- bind_rows(holes_2d_geo, holes_2d_geo_polish) %>% 
  explore_trace_interp(col = method) + ggtitle("search_geodesic")

p2 <- bind_rows(holes_2d_better_max_tries, holes_2d_better_max_tries_polish) %>% 
  explore_trace_interp(col = method) + ggtitle("search_better")

@@

```{r sample-code, eval = FALSE, echo = TRUE}
set.seed(123456)
holes_2d_geo <- animate_xy(data_mult[,c(1,2, 7:10)],tour_path = 
                             guided_tour(holes(), d = 2, 
                                         search_f = tourr:::search_geodesic),
                           rescale = FALSE, verbose = TRUE)

@@

The following example conducted a 2D projection on the larger dataset using search better with different configurations. `max.tries` is a hyperparameter that controls the maximum number of try without improvement and its default value is 25. As shown in Figure \ref{fig:trace-compare}, after polishing, both trials attain the same index value. However, a small `max.tries` of 25 is not sufficient for the algorithm to find the true maximum. This is because 25 tries is not sufficient for the 2D searching space.

```{r trace-compare, fig.cap="\\label{trace-compare}Breakdown of index value when using different max.tries in search better in conjunction with search polish. Both attain the same final index value after the polishing while using a max.tries 25 is not sufficient to find the ture maximum."}

p1 <- bind_rows(holes_2d_better, holes_2d_better_polish) %>% 
  explore_trace_interp(col = method) + ggtitle("max.tries = 25")

p2 <- bind_rows(holes_2d_better_max_tries, holes_2d_better_max_tries_polish) %>% 
  explore_trace_interp(col = method) + ggtitle("max.tries = 500")

@@

*Example 4: The neighbourhood parameter alpha* Add an example on comparing the neighbourhood parameter in serach_better & search_posse.

```{r nrow, echo = TRUE}
nrow(holes_2d_better_max_tries)
nrow(holes_2d_pos)
```

```{r alpha}
dt <- holes_2d_better_max_tries %>%
  filter(info != "interpolation") %>% 
  mutate(id = row_number())

p1 <- dt %>%
  ggplot(aes(x = as.factor(tries), y = alpha)) +
  geom_jitter(aes( col = as.factor(alpha))) +
  geom_line(data = dt %>% group_by(tries) %>% filter(index_val == max(index_val)),
            aes(group = 1)) + 
  theme(legend.position = "none")

p2 <- dt %>%
  ggplot(aes(x = as.factor(tries), y = alpha,)) +
  geom_jitter(aes(col = as.factor(alpha))) +
  geom_line(data = dt %>% group_by(tries) %>% filter(index_val == max(index_val)),
            aes(group = 1))  + 
  theme(legend.position = "none")

*Example 5 PCA* refine the example of matrix parameter exploration

```{r pca, echo = TRUE}
holes_1d_geo %>% explore_proj_pca(col = info) 
```

# Real-time animated diagnostic plots

```{r pca-animated, echo = TRUE, eval = FALSE}
holes_1d_geo %>% explore_proj_pca(animate = TRUE, col = info)
```

@@

Everything is coded up in a package.

\clearpage

### 2020-05-26 paper/paper.tex
reorder sections and plots

\includegraphics{paper_files/figure-latex/unnamed-chunk-3-1.pdf}

@@

\begin{verbatim}
## # A tibble: 5 x 7
##   basis             index_val tries info           loop method           id
##   <list>                <dbl> <dbl> <chr>         <dbl> <chr>         <int>
## 1 <dbl[,2] [6 x 2]>     0.804     1 start            NA <NA>              1
## 2 <dbl[,2] [6 x 2]>     0.793     1 random_search     1 search_better     2
## 3 <dbl[,2] [6 x 2]>     0.784     1 random_search     2 search_better     3
## 4 <dbl[,2] [6 x 2]>     0.773     1 random_search     3 search_better     4
## 5 <dbl[,2] [6 x 2]>     0.795     1 random_search     4 search_better     5
\end{verbatim}

\hypertarget{visual-methods}{%
\section{Visual methods}\label{visual-methods}}

Given all the information of interest in a global object, the next thing
is to design its visual representation that can diagnose our algorithm.
In an iterative algorithm, one would be interested to know how one
parameter changes as the algorithm iterates. The parameter could be
could be the decision variable, the value of the optimisation function
or other parameter that facilitate the algorithm. In projectio pursuit
guided tour, apart from the decision variable projection basis, the
value of index function (\texttt{index\_val}), we are also interested to
explore the effect the different searching methods, the neighbourhood
parameter alpha, and the stage a particular observation is in
(\texttt{info}). These are the variables that will be mapped into the
diagnostic plot. The global object also has its time series nature since
the observations are recorded as the algorithm progresses and thus can't
be switch in rows. This time series structure is always hierachical and
nested since each row can be labelled with the smallest unit \texttt{id}
and up by the iterative structure of the algorithm. Take our example, in
the global object, each row has an \texttt{id} label which is the
smallest unit the observation is ordered. A larger ordering unit is
\texttt{tries} since it is updated everytime a new target basis is
found. A nested ordering unit is \texttt{loop}, which increases by one
as searching method iterates and starts over at a new \texttt{tries}.
These features explain the definition of the global object for
projection pursuit guided tour in Figure @ref(fig:glb-obj).

\begin{figure}
\includegraphics[width=1\linewidth,height=0.2\textheight]{/Users/hzha400/Documents/3.PhD/paper-tour-vis/figures/global_obj} \caption{this is xxxx}\label{fig:glb-obj}
\end{figure}

\emph{The examples and results below still need to be modified as the
development / modification of both ferrn and tourr package}.

@@

A comparison of using scatter plot (all point geometry) and my new
design is shown in Figure @ref(fig:explore-all-search). As we can see
the points for the first few tries on hte scatter plot are all squeezed
in a tiny region, being nearly unseeable. While the plot on the right
balances out the points in each \texttt{tries}. By linking the updating
points for each \texttt{tries}, we observe that the largest improvement
occurs in \texttt{tries\ =\ 5} where the number of searching points
dramastically increased from 11 points in \texttt{tries\ =\ 4} to 86
points in \texttt{tries\ =\ 5}.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/explore-all-search-1.pdf}
\caption{This is xxx}
\end{figure}

@@

EXAMPLE: prevention on the decrese of interpolated value - interruption

EXAMPLE: comparison of interpolation in noisy index function

\includegraphics{paper_files/figure-latex/unnamed-chunk-7-1.pdf}

@@

EXAMPLE: polishing - add method : compare with max.tries and without for
search\_better.

EXAMPLE: add alpha: compare the cooling system of the neighbourhood
parameter in serach\_better \& search\_posse.

\begin{verbatim}
## [1] 1531
\end{verbatim}

\begin{verbatim}
## [1] 959
\end{verbatim}

\includegraphics{paper_files/figure-latex/unnamed-chunk-9-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{holes_1d_geo }\OperatorTok{%>%}\StringTok{ }\KeywordTok{explore_proj_pca}\NormalTok{() }
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: The `x` argument of `as_tibble.matrix()` must have column names if `.name_repair` is omitted as of tibble 2.0.0.
## Using compatibility `.name_repair`.
## This warning is displayed once every 8 hours.
## Call `lifecycle::last_warnings()` to see where this warning was generated.
\end{verbatim}

\includegraphics{paper_files/figure-latex/unnamed-chunk-10-1.pdf}

\hypertarget{animating-plots}{%
\section{Animating plots}\label{animating-plots}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{holes_1d_geo }\OperatorTok{%>%}\StringTok{ }\KeywordTok{explore_proj_pca}\NormalTok{(}\DataTypeTok{animate =} \OtherTok{TRUE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{finding-errors-and-developing-improvements}{%
\section{Finding errors and developing
improvements}\label{finding-errors-and-developing-improvements}}

The visualisation methods introduced above allow us to assess the
performance of each optimisation routine and thus provide improvments.

\hypertarget{interrupt}{%
\subsection{Interrupt}\label{interrupt}}

The left panel of Figure @ref(fig:interruption) presents the trace plot
of the interpolated basis using \texttt{search\_better} to optimise the
holes index (2D projection using the larger dataset). Tour interpolates
from the current basis to the target basis, which has been found to have
a higher index value by projection pursuit. The target basis will then
be sent to the projection pursuit as the current basis to find the next
target basis. We can observe from the plot that there are basis with
even higher index value on the interpolation path. These bases could be
used to search for new basis in the next round. Therefore, an
interruption is constructed to only take interpolated basis up to the
point where the index value stops increasing and the last basis is taken
as the current basis for the next round of search. After implementing
the interruption, the tracing plot with the same configuration is shown
on the right panel. Rather than interpolate to the target basis, the
interruption interrupt the process after id = 60 and proceeds the next
round of search from the interpolated basis. Taking advantage of the
interpolated basis results in a higher index value in the end with fewer
steps.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/interruption-1.pdf}
\caption{\label{interruption} Trace plots of the interpolated basis with
and without the interruption. The interruption stops the interpolation
when the index value starts to decrease, see the difference at id being
around 60. The implementation of the interuption finds an ending basis
with higher index value using fewer steps.}
\end{figure}

Further the case when the index function is not smooth, the
interpolation may not attain -\textgreater{} modification

\hypertarget{polish}{%
\subsection{Polish}\label{polish}}

In principle, all the optimisation routines should present the same
output on the same problem. In Figure @ref(fig:trace-compare), red dots
shows the trace of the interpolated basis using
\texttt{search\_geodesic} and \texttt{search\_better} (with max.tries =
100), respectively, on the 2D projection problem. We can observe that
they attain slightly different ending index value, which is not ideal.
This motivates the creation of a polishing search that polishes the
ending basis and achieves unity on different methods.

\includegraphics{paper_files/figure-latex/unnamed-chunk-12-1.pdf}

@@

The following example conducted a 2D projection on the larger dataset
using search better with different configurations. \texttt{max.tries} is
a hyperparameter that controls the maximum number of try without
improvement and its default value is 25. As shown in Figure
@ref(fig:trace-compare), after polishing, both trials attain the same
index value. However, a small \texttt{max.tries} of 25 is not sufficient
for the algorithm to find the true maximum. This is because 25 tries is
not sufficient for the 2D searching space.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/trace-compare-1.pdf}
\caption{Breakdown of index value when using different max.tries in
search better in conjunction with search polish. Both attain the same
final index value after the polishing while using a max.tries 25 is not
sufficient to find the ture maximum.}
\end{figure}

\hypertarget{posse}{%
\subsection{posse?}\label{posse}}

search\_better annd search\_geodesic methods are not doing good on 2d
projection -\textgreater{} see the simple case above: abs best is 0.96
while they only get to 0.88-ish. Would be worse for higher dimension.
thus search\_posse. get 0.95 and then polish to 0.96 :)

>>>>

\includegraphics{paper_files/figure-latex/origin-data-1.pdf}

@@

\begin{verbatim}
## # A tibble: 5 x 8
##   basis             index_val tries info           loop method       alpha    id
##   <list>                <dbl> <dbl> <chr>         <dbl> <chr>        <dbl> <int>
## 1 <dbl[,2] [6 x 2]>     0.804     1 start            NA <NA>           0.5     1
## 2 <dbl[,2] [6 x 2]>     0.793     1 random_search     1 search_bett~   0.5     2
## 3 <dbl[,2] [6 x 2]>     0.784     1 random_search     2 search_bett~   0.5     3
## 4 <dbl[,2] [6 x 2]>     0.773     1 random_search     3 search_bett~   0.5     4
## 5 <dbl[,2] [6 x 2]>     0.795     1 random_search     4 search_bett~   0.5     5
\end{verbatim}

\hypertarget{post-run-static-diagnostics-plots}{%
\section{Post-run static diagnostics
plots}\label{post-run-static-diagnostics-plots}}

Given all the information of interest in a global object, the next thing
is to design its visual representation that can diagnose our algorithm.
In an iterative algorithm, one would be interested to know how one
parameter changes as the algorithm iterates. The parameter could be
could be the decision variable, the value of the optimisation function
or other parameter that facilitate the algorithm. In projectio pursuit
guided tour, apart from the decision variable projection basis, the
value of index function (\texttt{index\_val}), we are also interested to
explore the effect the different searching methods, the neighbourhood
parameter alpha, and the stage a particular observation is in
(\texttt{info}). These are the variables that will be mapped into the
diagnostic plot. The global object also has its time series nature since
the observations are recorded as the algorithm progresses and thus can't
be switch in rows. This time series structure is always hierachical and
nested since each row can be labelled with the smallest unit \texttt{id}
and up by the iterative structure of the algorithm. Take our example, in
the global object, each row has an \texttt{id} label which is the
smallest unit the observation is ordered. A larger ordering unit is
\texttt{tries} since it is updated everytime a new target basis is
found. A nested ordering unit is \texttt{loop}, which increases by one
as searching method iterates and starts over at a new \texttt{tries}.
These features explain the definition of the global object for
projection pursuit guided tour in Figure \ref{fig:glb-obj}.

\begin{figure}
\includegraphics[width=1\linewidth,height=0.2\textheight]{/Users/hzha400/Documents/3.PhD/paper-tour-vis/figures/global_obj} \caption{\label{glb-obj}this is xxxx}\label{fig:glb-obj}
\end{figure}

@@

A comparison of using scatter plot (all point geometry) and my new
design is shown in Figure \ref{fig:points}. As we can see the points for
the first few tries on hte scatter plot are all squeezed in a tiny
region, being nearly unseeable. While the plot on the right balances out
the points in each \texttt{tries}. By linking the updating points for
each \texttt{tries}, we observe that the largest improvement occurs in
\texttt{tries\ =\ 5} where the number of searching points dramastically
increased from 11 points in \texttt{tries\ =\ 4} to 86 points in
\texttt{tries\ =\ 5}.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/points-1.pdf}
\caption{\label{points} This is xxx}
\end{figure}

@@

\emph{Example 1: Interruption} The left panel of Figure
\ref{fig:interruption} presents the trace plot of the interpolated basis
using \texttt{search\_better} to optimise the holes index (2D projection
using the larger dataset). Tour interpolates from the current basis to
the target basis, which has been found to have a higher index value by
projection pursuit. The target basis will then be sent to the projection
pursuit as the current basis to find the next target basis. We can
observe from the plot that there are basis with even higher index value
on the interpolation path. These bases could be used to search for new
basis in the next round. Therefore, an interruption is constructed to
only take interpolated basis up to the point where the index value stops
increasing and the last basis is taken as the current basis for the next
round of search. After implementing the interruption, the tracing plot
with the same configuration is shown on the right panel. Rather than
interpolate to the target basis, the interruption interrupt the process
after id = 60 and proceeds the next round of search from the
interpolated basis. Taking advantage of the interpolated basis results
in a higher index value in the end with fewer steps.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/interruption-1.pdf}
\caption{\label{interruption}Trace plots of the interpolated basis with
and without the interruption. The interruption stops the interpolation
when the index value starts to decrease, see the difference at id being
around 60. The implementation of the interuption finds an ending basis
with higher index value using fewer steps.}
\end{figure}

\emph{Example 2: Noisy index function} Add an example on noisy function

\includegraphics{paper_files/figure-latex/interpolation-1.pdf}

@@

\emph{Example 3: Polish} In principle, all the optimisation routines
should present the same output on the same problem. In Figure
\ref{fig:trace-compare}, red dots shows the trace of the interpolated
basis using \texttt{search\_geodesic} and \texttt{search\_better} (with
max.tries = 100), respectively, on the 2D projection problem. We can
observe that they attain slightly different ending index value, which is
not ideal. This motivates the creation of a polishing search that
polishes the ending basis and achieves unity on different methods.

\includegraphics{paper_files/figure-latex/polish-1.pdf}

@@

The following example conducted a 2D projection on the larger dataset
using search better with different configurations. \texttt{max.tries} is
a hyperparameter that controls the maximum number of try without
improvement and its default value is 25. As shown in Figure
\ref{fig:trace-compare}, after polishing, both trials attain the same
index value. However, a small \texttt{max.tries} of 25 is not sufficient
for the algorithm to find the true maximum. This is because 25 tries is
not sufficient for the 2D searching space.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/trace-compare-1.pdf}
\caption{\label{trace-compare}Breakdown of index value when using
different max.tries in search better in conjunction with search polish.
Both attain the same final index value after the polishing while using a
max.tries 25 is not sufficient to find the ture maximum.}
\end{figure}

\emph{Example 4: The neighbourhood parameter alpha} Add an example on
comparing the neighbourhood parameter in serach\_better \&
search\_posse.

\begin{verbatim}
## [1] 1529
\end{verbatim}

\begin{verbatim}
## [1] 1056
\end{verbatim}

\includegraphics{paper_files/figure-latex/alpha-1.pdf}

\emph{Example 5 PCA} refine the example of matrix parameter exploration

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{holes_1d_geo }\OperatorTok{%>%}\StringTok{ }\KeywordTok{explore_proj_pca}\NormalTok{(}\DataTypeTok{col =}\NormalTok{ info) }
\end{Highlighting}
\end{Shaded}

\includegraphics{paper_files/figure-latex/pca-1.pdf}

\hypertarget{real-time-animated-diagnostic-plots}{%
\section{Real-time animated diagnostic
plots}\label{real-time-animated-diagnostic-plots}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{holes_1d_geo }\OperatorTok{%>%}\StringTok{ }\KeywordTok{explore_proj_pca}\NormalTok{(}\DataTypeTok{animate =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{col =}\NormalTok{ info)}
\end{Highlighting}
\end{Shaded}

\hypertarget{vis-package}{%
\section{Vis package}\label{vis-package}}

Everything is coded up in a package.

\clearpage
